---
title: High Poll Engagement but sharply Declined in April 2020
author: "Hong Pan"
date: "`r format(Sys.time(), '%d %B %Y')`"

abstract: The line chart and the table created help illustrate that the poll response rate has started to decline in 2019. Declining poll response rates may cause non-response bias, which misunderstanding the real feeling and thinking of people. Two bar charts created help show largest people have a question about Front Yard Parking. Let the government know where people are dissatisfied with the city.
thanks: 'Code and data are available at: https://github.com/HongTrista/folder.'
bibliography: references.bib

output:
  bookdown::pdf_document2:
  toc: no
  fig_cap: yes
  keep_tex: yes
  includes:
    in_header:my_header.tex

header-includes:
 - \usepackage{float}
 - \floatplacement{figure}{H}
 - \floatplacement{table}{H}

 
 
---

```{r setup, include=FALSE}
#install all packages 
knitr::opts_chunk$set(echo = TRUE, fig.pos= "h")
chooseCRANmirror(graphics=FALSE, ind=1)


install.packages("ggplot2") # for drawing nice figures
library(ggplot2)

install.packages("tidyverse") # for filtering data
library(tidyverse)

install.packages("readr") # for read the dataset
library(readr)

install.packages("bookdown") # for cross referencing figures and tables
library(bookdown)


install.packages("kableExtra") # for creating table
library(kableExtra)

install.packages("zoo")# for editing the time variable
library(zoo)

install.packages("ggpubr")
library(ggpubr)

```


# Introduction

Low poll engagement may cause non-response bias, which would misunderstanding the real feeling and thinking of people.[@Cite_Surveys] Public polls belong to human research surveys to help us know how a population thinks about any specific topic. The trained interviewers will ask questions to people chosen randomly from the population being measured. The interviewees' answers will be interpreted and help to make a final decision on the application applied.[@Cite_Wikipedia] The main benefit for people from the public polls is that it gives regular people a chance to be heard instead of letting only media stars speak on behalf of all.[@Cite_gallup]


# need to edit
After knowing the definition and importance of public polls, I want to look at how people's positively toward public polls by creating a variable called engagement rate in this paper. I construct a line chart to show the average engagement rate changes from 2015 to 2020. The graph shows that the engagement rate slightly rises from 2015 to 2019, but a sharp decrease from 2019 to 2020. Then, I create a table to illustrate the average engagement rate for each type of application,  and I find that Permit Parking has the highest average engagement rate. To know more information in detail, I draw two histograms to display how many applicants for each type and the number of results, whether the application has passed. The graphs show that most people have a problem with Front Yard Parking, but it has the highest pass rate.

The remainder of the paper is structured as follows: Section 2 discusses the variables in the data set, Section 3 presents the figures and tables with their explanations,and finally Section 4 provides all the references.


# Data
```{r,include=FALSE}
#Import cleaned dataset
clean_data<-read_csv(url("https://raw.githubusercontent.com/HongTrista/folder/main/input/clean_data.csv"))
```
The analysis for this paper done using R [@Cite_R]and several packages, which listed as followed: 'ggplot2' helps to visualize the data in figures[Cite_ggplot2], 'tidyverse' used for data manipulation[@Cite_tidyverse], 'readr' used for import data set from URL by R[@Cite_readr], 'bookdown' used for cross-referencing figures and tables[@Cite_bookdown],'kableExtr' used for creating a table [@Cite_kableExtr], and 'lubridate' used to edit the time variable.[@Cite_zoo]  The data set, Polls Conducted by the City, I used for analysis in the paper is from the City of Toronto Open Data Portal.[@Cite_Dataset] 

The main goal of creating the dataset is to analyze the poll engagement in Toronto. The dataset is free to the public and starts on April 1, 2015. When the City Clerk's Office receives an application, a poll will distribute to all the people who may be influenced in the region mentioned in the application. People have the right to participate in the poll or not, the number of people who do not mail the poll back, the address is wrong, and any information will be recorded in the dataset. Only the application which meets the required response rate will be processed to the next step. The data will be updated after the polls have been closed and after the certification has been made. As we mentioned before, a low response rate may cause non-response bias, which means the real feeling and thinking of a specific event will be misunderstood. For example, the article analysis of health problem with non-response bias pointed out that non-response was determined to contribute to underestimated health risks. The strength of the data set I used in the paper is that it set the minimum response rate for each application, which may prevent non-response bias to some extent.[@Cite_bias]

The data set after cleaning contains 6 variables with 922 conversations and no missing values. The explanations of each variable will be shown in the following:\
. Application_topic: Type of each application, which is a categorical variable with levels of "Front Yard Parking", "Traffic Calming," "Boulevard Cafe", "Business Improvement Area," and "Commercial Boulevard Parking."\
. Response_rate_met: Whether the number of ballots returned has met the required response rate, a categorical variable with values 'YES' and 'NO.'\
. Real_total_number: The number of total voters on the final poll list, which is a numerical variable.\
. Potential_total_number: The number of people residing within the poll boundary range, which is a numerical variable.\
. Date: The date of close, a time categorical variable from June 5, 2015, to Dec 30, 2020.\
. Final_result: The final result of the poll, which is a categorical variable with levels of "In favour', ' opposed,' and ' response rate not met.'\

```{r}
#Create a new column, response_rate.
clean_data<-clean_data%>%
  mutate(Response_rate=round((Real_total_number/Potential_total_number),3))
```

In order to analyze the real response rate for each application topic, I create a new variable, response_rate, based on the Real_total_number and Potential_total_number variables in the clean dataset.:
. Response_rate: Real_total_number divided by Potential_total_number




Table 1(Table \@ref(tab:table1)) shows the total number of application for each different topic, we can see that from year 2015 to 2020, the number of application about the problem with Front Yard Parking occupied half of the total application number, which is 510 in 922. We can deduce that most people have the problems about the issue of front yard parking. The figure 1(Figure \@ref(fig:Figure1)) illustrate a line chart shows the trend of the total application number from year 2015 to 2020 in each quarter. The line chart shows a downward slope, which means all topics the city organization cares about are gradually getting better because fewer and fewer application numbers are being received. This is a great sign for the city organization.

```{r table1,echo=FALSE}
#Create a table only show the type of topic and the total number of application per topic
table1<-clean_data%>%
  group_by(Application_topic)%>%
  count()

# Show the table
table1%>%
  kable(caption = "Total number of applications per topic",col.names = c("Application_topic","Number"))
```



```{r Figure1,fig.cap="Total number of application in each quarter",echo=FALSE,fig.height = 3, fig.width = 8}
#change the date to quarter form
clean_data<-clean_data%>%
  mutate(Date_quarter=as.yearqtr(Date, format = "%Y-%m-%d"))



#plot a figure to show the trend of total application along with time
ggplot(clean_data, aes(x=Date_quarter)) + 
  stat_count(geom='line', aes(y=..count..),size=1,color='blue')+
  ylab("Number of application")
```

```{r}
#To avoid messing up the original data set, duplicate the clean_data as tmp_data:
tmp_data<-clean_data

#create two new column, Date_month and Date_year.
tmp_data<-clean_data%>%
  complete(Date = seq.Date(min(Date), max(Date), by="day"))%>%  # create consistent date
  mutate(Date_month=format(as.Date(Date),"%Y-%m"),              # only includes the value of year and month.
         Date_year=format(as.Date(Date),"%Y"))                  #only includes the value of the year
```

The time range for the data in the dataset is from 2015 to 2020 last day. To know how people's attitudes towards the public polls, I draw a line chart to show the response rate trend, how many people actually engaged in the City's polls. Because according to each application, there will be a list of people selected to participate in the public polls, however, some people will refuse to participate. I want to indirectly understand people's attitudes towards the public polls by knowing the response rate.

The line chart (Figure \@ref(fig: Figure2)) shows that the response rate generally fluctuated around 0.8 from 2015 to April 2020. The relatively high engagement rate illustrates that people actively participate in the City's public polls in the past six years. The line sharply declined in April 2020 from 0.88 to 0.5 in October and bounced back to normal in November. As we all known, the covid-19 broke out in March in Toronto, which may be the reason influence the engagement sharply decline in April, and because the response rate quickly returned to normal levels in November. From this, it can be inferred that the drastic decline was not due to changes in people’s attitudes towards polls, but more data is needed to support this conjecture.

```{r Figure2,fig.cap="Average response rate per month",echo=FALSE,warning=FALSE,fig.height = 3, fig.width = 8}
# Draw the a line chart to show the trend of average response rate each month.

ggplot(data = tmp_data, aes(x = Date_month, y = Response_rate)) + 
   stat_summary(geom = "line", fun = mean,group=1,color='blue')+
  theme(axis.text.x = element_text(angle = 90))+
  ylab('Average Response_rate')


```

To know more about data, the graphs about different topics with whether the required response rate has been met or not, and with the final result situation for each topic been analyzed. From the left graph in figure 3(Figure \@ref(fig: Figure3)), Traffic Calming has the highest number of applications that do not meet the required response rate among all types, which is around half of the total applications in Traffic Calming topic. Meanwhile, Front Yard Parking has the highest application number that meets the required response rate, which is around 95% of the total applications on the topic of Front Yard Parking.

The applications which do not meet the required response rate will be given the final result of "No", then, the graph about the final result for the applications which meet the required response rate has been plotted on the left in figure 3(Figure \@ref(fig: Figure3)). The graph illustrates that Front Yard Parking has the highest pass rate by showing the highest proportion of result of "in favour," then, followed by Traffic Calming. Combined the information we explored out in table 1(Table \@ref(tab:table1)), which shows that almost half of the applications are about Front Yard Parking, we can infer that although most people have problems with front yard parking, it is the easiest to pass topic.



```{r Figure3,fig.cap="Combine two graphs to show information in detail",echo=FALSE,warning=FALSE}
# Create a graph showing the number of application for each topic by different result from whether the application meet the response rate requirement.
p1<-ggplot(clean_data, aes(x=Application_topic)) + 
  stat_count(geom='bar', aes(y=..count..),fill='purple')+
  facet_wrap(~Response_rate_met)+
  ylab("Number of application")+
  theme(axis.text.x = element_text(angle = 90))+
  ggtitle('Topic with response_rate_met')


# Create a graph showing the number of application for each topic for application which meets the required response rate.

p2<-clean_data%>%
  filter(Response_rate_met=="Yes")%>%
  ggplot(aes(Application_topic, fill =Final_result)) + 
  geom_bar()+
  theme(axis.text.x = element_text(angle = 90))+
  ylab("Application Number")+
  ggtitle('Topic with final result')
  
ggarrange(p1, p2, ncol = 2, nrow = 1)

```

While the poll engagement behaves great in Toronto, shown by the paper's result. However, the result is not representative due to the limitations of the dataset using for analysis. The first point is that the application volume for each topic is not close to equal. For instance, almost half of the application is about front yard parking, which may cause the result unreliable. Also, the date of collecting data is inconsistent, which may hide the information behind. Finally, the required response rate for each application is different, which will influence the analysis. The information about how to generate the required response rate should be explained.



















































