---
title: The type of traffic calming safety zone has the best poll engagement by least
  application number
author: "Hong Pan"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  bookdown::pdf_document2:
  toc: no
abstract: null
thanks: 'Code and data are available at: https://github.com/HongTrista/folder.'
bibliography: output/paper/references.bib
---

```{r setup, include=FALSE}
#Import packages 
knitr::opts_chunk$set(echo = TRUE)
chooseCRANmirror(graphics=FALSE, ind=1)
install.packages("ggplot2")
```


```{r,echo=FALSE,include=FALSE}
#Import cleaned dataset
library(readr)
new_data<-read_csv(url("https://raw.githubusercontent.com/HongTrista/folder/main/input/raw_dataset.csv"))
```



## Introduction

The paper aims to investigate people's attitudes towards city polls. According to Wikipedia's definition [@Cite_Wikipedia], we know that an opinion poll is a type of human research survey to grab people's views regarding a particular topic. The interviewers who have been trained will ask questions to people chosen randomly from the population being measured. The answers will be interpreted and help to make a final decision on the application being applied.

According to the article published by Gallup [@Cite_gallup], we know the importance of poll. The main benefit of doing a poll is to help regular people be heard. The article pointed out that polls can help us know the proportion of a population with a specific viewpoint. Meanwhile, polls are a kind of measurement tool that can explain how a population thinks about any given topic, which can help different cultures understand one another because it gives the people a chance to speak for themselves instead of letting only vocal media stars speak on behalf of all. Because we know the polls are important for the city, I want to know what kind of application most people care about and the pass rate. Moreover, from 2015 to 2019, does people's engagement rate for polls have been improved or not.

For the rest of my paper, I will describe the dataset I used to analyze in the "Data" section. The content includes the descriptions of each variable, the source of the data set, and the data set's size. The findings of my analysis and the graphs and tables used to illustrate my results will be displayed in the section. The "Reference" section will contain all the citation information.



## Data

The dataset, polls conducted by the City I used for analysis in the paper is from the City of Toronto Open Data Portal. The dataset was created for getting the opinions of residents or businesses on different types of topics covered by a City by-law. The methodology of the data being collected is that when an application is submitted, people in the affected area will be given a poll conducted by the City by mail. Only the application that meets benchmarks determined by specific by-law or city policy will be assigned for positive, and City Council will approve the result. The raw dataset contains 25 variables with around 1000 records and some missing values in a specific column. The labelled columns include the type of application, number of blank ballots, number of ballots returned, number of ballots returned by Canada Post as not delivered, the date the poll is open to the public, so on so forth.

The purpose of the paper is to investigate changes in people's attitudes towards polls and the types of applications. The columns I interested in being selected created as a new dataset, which will be listed as followed: the type of application, the date the poll is open to the public, the final result of each application, the number of total voters on the final poll list and the number of people residing within poll boundary range. I also created a new column named engagement rate, which is used to calculate by using the number of a total voter on the final poll list divided by the number of people residing within the poll boundary range. The new dataset used for the analysis has 6 variables with around 1000 records and without missing or null values.





Our data is of applications(Figure \@ref(fig:Figure1))
```{r Figure1,fig.cap="Type of Applications",echo=FALSE,warning=FALSE}
ggplot(new_data)+
  geom_bar(aes(x=Type),fill='Orange')+
  theme(axis.text.x = element_text(angle = 90))
```

PLZ see the second figure (Figure \@ref(fig:Figure_2))
```{r Figure2,fig.cap="Typf of Application with final result",echo=FALSE,warning=FALSE,fig.align='center'}
ggplot(new_data, aes(Type, fill =Result)) + 
  geom_bar()+
  theme(axis.text.x = element_text(angle = 90))

```



The table showed below (Table \@ref(tab:table1))
```{r table1,warning=FALSE}

table1<-new_data%>%
  group_by(Type)%>%
  summarize(
    Mean=round(mean(Engagement_rate),3),
    Std_dev=round(sd(Engagement_rate),3)
  )%>%
  arrange(desc(Mean))

table1 %>% 
  knitr::kable(caption = "The engagment rate for each type of application")

```





#References
@R